---
title: "My Final Project Template - First Draft"
author: "Amanda Waggoner"
subtitle: Final project template for the GEO511 class
editor_options: 
  chunk_output_type: console
---

# Introduction

Brooklyn, NY is one of the major boroughs of New York City, NY. Known
for its diverse populace, art and music scene, the borough has become a
hub for many to live and explore the area. In the mid-1830s to the
beginning of the 1900s, Brooklyn was a hub for many immigrants to start
their lives together. A multicultural melting pot, just like the rest of
New York City, Brooklyn contained Blacks, Asians, Latinos, and European
migrants within its boundaries. However, New York City’s demography
shifted with the rise of the industrial revolution and the impacts of
World Wars I/II. Economically, many shipping and manufacturing
industries left the city as a whole, causing crime, job losses, and
people moving out from the city (Freudenheim 14).

  Because of these shifts, throughout the 1950s, 60s and 70s, Brooklyn kept declining in population. However, immigration ensued as people from other countries kept coming to America to find new ways of life. Brooklyn began to return back to its original prowess in the mid-1980s, as parks, buildings, homes, etc. were revitalized by wealthier patrons moving into the area. Gentrification ensued, and urban renewal policies began to take foot in many neighborhoods within Brooklyn. From the 1980s onward, toward the new millennium, Brooklyn began to become further and further gentrified and was dubbed one of the “most desirable places to live” during the 2010s (Freudenheim 14). 

  How did these changes impact the Black communities living within Brooklyn? Initially, during the late 1800s, as freed slaves began to escape and live towards the north, Black populations rose in many urban areas like Philadelphia, Washington, D.C., and other cities across the United States. New York was another city where freed Blacks lived and escaped towards, and similar to Harlem, Brooklyn was another location within New York City where Blacks felt safe to establish community in. Because of the community that Blacks established in Brooklyn, many types of businesses: (churches, restaurants, schools, nightlife, etc.), were established for and by Black Brooklynites. 

  As time progressed, closer to the new millennium, white gentrifiers
replaced and outnumbered the Black populace of Brooklyn. Many formerly
majority Black neighborhoods within Brooklyn were becoming increasingly
more populated by “upper-class whites” (Chronopoulos 2020). Because of
these changes, many Black Brooklynites felt displaced and removed from
the communities they established and created, feeling as if their
legacies were being removed from the neighborhoods they inhabited.
Gentrification not only displaced Black inhabitants from their homes but
also displaced Black Brooklynites from their businesses and general
sense of community (Valli 2016).


# Materials and methods

  In order to accomplish my findings, I ended up creating an application through Yelp's API for Developers. That application was the basis for my API Key and search conditions that I used to apply to my code. Then, within my code, I added sections where I could apply specific terms for my search parameters. (This will be demonstrated within my code chunks below.) I ended up focusing on the search term, "African-American", and then looking for categories applicable to nightlife, such as, "bars, venues", etc. 

Data: The data that I used to create maps were all open-source data. Ggmap, Ggplot2 and Leaflet were my main sources of map creation. I installed the packages and created maps based on the data points I extracted from my Yelp search. However, my biggest issue that I need help with is pulling the coordinate data directly from my Yelp search onto my map.

Challenges: When I was creating my map, I pulled the data from Yelp into a separate .csv file and then re-loaded it into R. However, the data was not fully reading, so in order to accomplish this first draft, I manually added Markers and Popups as points onto my map. I would like assistance in remedying this issue, by directly have all of the information that Yelp pulls from its search into my Markers as Popup information. 


Load any required packages in a code chunk (you may need to install some packages):

```{r, message=F, warning=F}
library(tidyverse)
library(leaflet)
library(kableExtra)
library(sf)
library(jsonlite)
library(ggplot2)
library(leaflet)

# Load yelpr package
library(yelpr)

# Assign App Key
key <- "ovIH-U3kauQ5ikHV5951RqsOq81q4MycWiu5xIsFCzd_c2zKxAwUdhb-SDvOeJ9Wrp_3rSVS3z5PuQDqfbl9grNOI3SFeHsOViv2eXZMnus6NlYyWs3gURZP_m-UYXYx"

# Search businesses with keyword 'black' in 'Brooklyn, New York'
business_bk <- business_search(api_key = key,
                               location = 'Brooklyn, NY',
                               term = "African American",
                               categories = 'venues, bars, African',
                               limit = 10)  
                                  
business_bk_spatial <- business_bk$businesses %>% as.data.frame() %>% 
  jsonlite::flatten(recursive = TRUE) %>% unnest(cols="coordinates.latitude") %>%
  st_as_sf(coords=c("coordinates.longitude", "coordinates.latitude"))
business_bk_spatial<-business_bk_spatial %>% mutate(popup=paste0("<br/><b><a href='",url,"'>",name,"</a"))

View(business_bk_spatial)

# Test plot
ggplot(business_bk_spatial)+geom_sf()

knitr::opts_chunk$set(cache=TRUE)  # cache the results for quick compiling
```

# Results

In terms or results, I've generated two maps for the purposes of this peer review. The first map is just showing the location of Brooklyn, NY in New York state. The second map is showing the results of my Yelp API search with the names as Popups. However, I want to fix this and layers of information as clickable popups to the data. For example, I want to add Markers with the business' URL links, information, and other facts.

```{r, fig.width=6, fig.height=3, fig.cap="Map of Brooklyn and African-American Brooklyn Music Venues/Nightlife"}
# Mapping the data extracted from the Yelp Fusion API


# Create a map of African-American businesses in Brooklyn, NY from the Yelp API



# Select different basemaps
business_bk_spatial %>%
  leaflet() %>%
  addProviderTiles(providers$Esri.WorldImagery, group = "World Imagery") %>%
  addProviderTiles(providers$Esri.WorldStreetMap, group = "World Street Map") %>%
  addLayersControl(baseGroups = c("World Imagery","World Street Map")) %>%
  # Add the businesses as Markers
  addCircleMarkers(popup = business_bk_spatial, fillOpacity = 0.5)%>%
 setView(lat = 40.650002, lng =-73.949997, zoom = 9.5)

```



# Conclusions

I have not completed the analysis portion of this research yet, so I do not have any conclusive findings as of yet. However, what I can attest to is that there are not a lot of Black-owned music venues left within this small amount of data. What mostly appears when I've used these terms for my search are museums and some bars, but not much in the way of music-specific venues. 

# References (as of now)

1. https://github.com/OmaymaS/yelpr
2. https://www.yelp.com/profile?fsid=gLo385y0jkTIMh1kCXgjjw
3. https://towardsdatascience.com/making-interactive-maps-in-r-with-less-than-15-lines-of-code-bfd81f587e12
4. http://remi-daigle.github.io/GIS_mapping_in_R/
5. https://rstudio.github.io/leaflet/markers.html
6. https://map-rfun.library.duke.edu/01_georeference.html

Final Project

